---
title: "Books"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Books}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```
```{r, include = FALSE}
knitr::opts_chunk$set(
  dev = "png",
  dpi = 150,
  fig.asp = 0.618,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center",
  collapse = TRUE,
  comment = "#>"
)
```
<br>
<br>

# `r colorize("New Contributions of Functional Data Analysis in Statistical Process Control","#1CA666")`
<br>

<object data="199451588.pdf" width=775, height=550></object>

<br>

### `r colorize("Cite","#1CA666")`

<p style="text-align:justify;">Sánchez, M. F. (2019). New Contributions of Functional Data Analysis in Statistical Process Control.</p>


# `r colorize("New methodology for the detection of inconsistent results in interlaboratory studies using functional data analysis","#1CA666")`

<br>

<object data="génesis_moreno_y_cristian_solórzano_-_trabajo_con_correciones.pdf" width=775, height=550></object>

<br>

### `r colorize("Cite","#1CA666")`

<p style="text-align:justify;">Solorzano Maya, C. I., & Moreno Armijos, G. C. (2022). New methodology for the detection of inconsistent results in interlaboratory studies using functional data analysis (Bachelor's thesis, Quito: EPN, 2022).</p>

# `r colorize("Application of a new methodology based on the Bootstrap method for the detection of atypical results in interlaboratory studies: A practical case in clinical laboratories","#1CA666")`

<br>

<object data="T-ESPE.pdf" width=775, height=550></object>

<br>

### `r colorize("Cite","#1CA666")`

<p style="text-align:justify;">BOSSANO CAVE, J. R. (2019). VICE-RECTORATE FOR RESEARCH, INNOVATION AND TECHNOLOGY TRANSFER.</p>


