---
title: "Databases"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Databases}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```
```{r, include = FALSE}
knitr::opts_chunk$set(
  dev = "png",
  dpi = 150,
  fig.asp = 0.618,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center",
  collapse = TRUE,
  comment = "#>"
)
```
<br>

# `r colorize("1. Examples of Interlaboratory Studies","#1CA666")`

<p style="text-align:justify;"> An Interlaboratory Study evaluates the analytical methods performed by laboratories, either for the evaluation of the efficiency of the laboratories involved, or for the performance of an experimental procedure, or for the validation of a standard guideline. For example, to show the application of consistency test, the `ILS`, package contains the `Glucose` dataset, avalaible on ASTM E-691 that corresponds to the results of a clinical test. Likewise, from a study of the properties of the calcium oxolate material, three datasets (`IDT`, `TG`, `DSC`) were obtained, and they were incorporated into the package.</p>

<br>

## `r colorize("1.2. Clinical study of blood glucose measurement","#1CA666")`

<p style="text-align:justify;"> The `Glucose` dataset corresponds to the serum glucose test (measurements of the concentration of glucose in the blood used to control the diabetes). In the study, eight laboratories where involved, and five different tests were performed on blood samples labelled with different references, ranging from a low sugar content to a very high one. Three replicates were obtained for each sample.</p>

<p style="text-align:justify;"> Each of these laboratories measured five different concentration levels (A, B, C, D, E) of a given material, and at each of these levels, three measurements were taken (3 replicates). Each laboratory provided a total of 15 measurements (3 for each level), therefore, with 8 laboratories involved, 120 measurements were obtained.</p>

<p style="text-align:justify;"> In order to access this dataset, the `ILS` package installing and loading is required. Once loading is performed, the `Glucose` `data.frame` object is called using the following instructions.</p>

```{r warning=FALSE,message=FALSE}
library("ILS")
data("Glucose", package = "ILS")
```
<p style="text-align:justify;"> The first step to perform an analysis with the `ILS` package consist on using the function `lab.qcdata()` (quality control data) that receives a data.frame as an argument. The first column of the data frame must contain the response variable, the second column accounts for the index of repetition for each laboratory, the third column includes the index of the material at which the test was performed, while the fourth column includes the index of the laboratory where the procedure was performed.</p>


<p style="text-align:justify;"> Afterward, the qcdata object, corresponding to the `lab.qcdata()` class, is developed. The descriptive statistics information of the dataset can be summarized by using the `summary()` function. Figure 1, shows the results of all laboratories.</p>



