---
title: "Interlaboratory Studies (ILS)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interlaboratory Studies (ILS)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```
```{r, include = FALSE}
knitr::opts_chunk$set(
  dev = "png",
  dpi = 150,
  fig.asp = 0.618,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center",
  collapse = TRUE,
  comment = "#>"
)
```
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{reference/figures/Encabezado_Article.png}
\caption{Ejemplar de tigre de Bengala}
\label{fig:tigre}
\end{figure}




# `r colorize("3. Standard Approach","#1CA666")`

<p style="text-align:justify;"> The ILS package provides two groups of functions made to detect outlying individual results (outlying replicates) and outlying laboratories: both for the scalar and the functional cases (Table 1). The ILS package offers graphical and analytical procedures (statistical hypothesis test) for this purpose.</p>

<br>

<center> **Table 1**: Functions incorporated to the ILS package to perform Interlaboratory Studies with a scalar and functional approach. </center>

|                 | **Technique**  | **Function**   | **Description**                                         |
|:----------------|:------------------|:--------------------|:------------------------------------------------|
|**Scalar**       | Plot              |`h.qcs, k.qcs`       | Mander's $h$ and $k$ statistics                 |
|**approach**     | Test              |`test.cochran`       | Cochran test                                    |
|                 |                   |`test.grubbs`        | Grubbs test                                     |
|                 |                   |`lab.aov`            | ANOVA                                           |
|**Funtional**    | Plot              |`h.fqcs, k.fqcs`     | Mandel's $H(x)$ y $K(x)$ functional statistics      |
|**approach**     | Test              |`mandel.fqcs`        | Mandel's functional test                        |

<br>

<p style="text-align:justify;"> As above mentioned, among the methodologies used to evaluate the consistency of laboratory results, we must highlight the r&R studies, which quantify the variability between laboratories (reproducibility) and variability between results (repeatability). The repeatability is the variability between the results of the independent tests obtained for each individual laboratory, i.e. the evaluation of the variability produced by the measurement system since the results are obtained by a single operator in each laboratory and in a short interval of time. On the other hand, the reproducibility refers to the variability between the re- sults of individual tests obtained in different laboratories, allowing to determine the bias.</p>

<br>

<p style="text-align:justify;">Accordingly with the repeatability and reproducibility concepts, Mandel's $h$ and $k$ statistics are used in ILS to detect laboratories that provide inconsistent results. The h statistic explains the variability between the laboratories, that is, estimates the bias, which is the difference of the means of each laboratory with respect to the global mean, while the k statistic estimates the variability within the laboratories, comparing the repeatability corresponding to each laboratory. The decision rule for detecting whether a laboratory is inconsistent is based on the comparison between the value of the $h$ or $k$ statistic and the critical value calculated with a significance level of $0.5%$, which is the one recommended by ASTM E-691.</p>

<br>
<p style="text-align:justify;">On the other hand, the `ILS` package performs the Cochran test to examine the consistency within a laboratory, whereas the Grubbs test is commonly used to examine consistency between laboratories. The Grubbs test can also be used as a consistency test for the results obtained in a laboratory using identical materials. These tests are recommended by ISO 5725-2.</p>

<br>

## `r colorize("3.1. Consistency tests","#1CA666")`

<p style="text-align:justify;">The basic statistical model proposed on ISO 5725-2 that estimate the accuracy and precision of an analytical method is:</p>

\begin{equation}
 y = m + B + \epsilon  (1)
\end{equation}

<p style="text-align:justify;">Where $m$ is the general mean for the material under analysis, $B$ is the laboratory bias component under repeatability conditions, and $\epsilon$ is the random error occurring in each measure under repeatability conditions. The repeatability variance $\sigma_r^2$ is estimated by $S_r^2$, which is the within-laboratory variance. On the other hand, the between-laboratory variance $\sigma_B^2$ is estimated by $S_B^2$, this variance is related to laboratory bias. The reproducibility variance $\sigma_r^2$ is given by:</p>

\begin{equation}
\sigma_R^2=\sigma_r^2+\sigma_B^2 
\end{equation}

<br>

<p style="text-align:justify;">Using the `ILS` package, one-way ANOVA analysis and mean comparison test can be performed. However, laboratories that present non-consistent results should be excluded from the ILS in advance. Accordingly, consistency tests and identidication of atypical results must be performed in advance of ANOVA analysis.</p>

<br>

<center>**Table 2**: ANOVA approach for the estimation of $S_r^2$ and $S_B^2$.</center>

| **Source**        | **Mean squares**  | **Estimate of**   |
|:-------------|:-----------------------------|:-------|
|Laboratory      | $MS_B=\frac{\displaystyle\sum_{i=1}^L n_i(\bar{y}_i-(\bar{y})^2)}{(L-1)}, \hspace{0.1cm}S_B^2=\frac{MS_B-MS_r}{\bar{n}}$ |$\sigma_r^2+\bar{n}\sigma_B^2$ | 
|Residual = repeatibility      | $MS_r=\frac{\displaystyle\sum_{i=1}^L\displaystyle\sum_{j=1}^{n_i} (y_{ij}-\bar{y}_i)}{(N-L)}, \hspace{0.1cm}d.f.=(N-L)$              |$\sigma_r^2$       | 


In Table(2), the one-way ANOVA approach results are shown, with 

\begin{equation}
  \bar{n}=\frac{1}{L-1}\left(\displaystyle\sum_{i=1}^L n_i-\frac{\displaystyle\sum_{i=1}^L n_i^2}{\displaystyle\sum_{i=1}^L n_i}\right), \hspace{0.1cm} \mbox{and} \hspace{0.1cm}N=\displaystyle\sum_{i=1}^L n_i. \hspace{0.1cm}\mbox{If}\hspace{0.1cm}S_B^2\leq 0, \mbox{set}\hspace{0.1cm}S_B^2=0 
\end{equation}

<p style="text-align:justify;">There are two possible scenarios in which the presence of outliers can be evaluated: the first is that the results of one laboratory deviates from the others in terms of precision, that is, when the measurements made by a laboratory differ signficantly with respect to the measurements obtained by other laboratories. The second scenario is related with the identification of outliers in a laboratory for a certain level. The statistics and tests recommended by ISO 5725-2 and ASTM E-691 are described below.</p>

<br>

### `r colorize("3.1.1. Mandel's h statistic and Grubbs test","#1CA666")`

<p style="text-align:justify;">Let $(x_1, x_2,\ldots, x_L)$ a sample of $L$ observations. The $x_l; l = 1, \ldots,L$ are modelled as realizations of random variables $X_l; l = 1, \ldots,L$  being identically and independently distributed according to the normal distribution $N(\mu, \sigma^2)$. We denote:</p>

\begin{equation}
\bar{X}=\frac{\displaystyle\sum_{l=1}^L X_l}{L} 
\end{equation}

<p style="text-align:justify;">as the mean of the $X_l$,</p>

\begin{equation}
 S^2=\frac{1}{L-1}\displaystyle\sum_{l=1}^L (X_l-\bar{X})^2 
\end{equation}

<p style="text-align:justify;">as the sample variance of the $X_l$.</p>

<p style="text-align:justify;">Mandel's h statistic is defined by:</p>

\begin{equation}
H_l=\frac{X_l-\bar{X}}{S};\hspace{0.1cm} l=1,\ldots,L 
\end{equation}

<p style="text-align:justify;">Which has the same distribution for all $l = 1, \ldots ,L$. The critical value is:</p>

\begin{equation}
h_{l;1-\frac{\alpha}{2}}=\frac{(L-1)t_{L-2;1-\frac{\alpha}{2}}}{\sqrt{L\left(t_{L-2;1-\frac{\alpha}{2}}^2+L-2\right)}};\hspace{0.1cm} l=1,\ldots,L 
\end{equation}

<p style="text-align:justify;">Whereby $t_{L-2;1-\frac{\alpha}{2}}$ is the $\left(1-\frac{\alpha}{2}\right)$ quantile of the $t$ distribution with $v = L−2$ degrees of freedom.</p>

<p style="text-align:justify;">For the case defined by $L$ laboratories that obtain n replicates each one, the $h$ statistic is defined by:</p>

\begin{equation}
h_{l}=\frac{d_l}{S_{\bar{x}}}=\frac{\bar{x}_l-m}{\sqrt{\displaystyle\sum_{l=1}^L \frac{(\bar{x}_l-m)^2}{L-1}}};l=1,\ldots,L
\end{equation}

<p style="text-align:justify;">Whereby $\bar{x}_l$ is the mean of the n results of each laboratory, and $m$ is the global mean of the results of the $L$ laboratories.<p>

<p style="text-align:justify;">A laboratory is detected as inconsistent when the value of the statistic $h_l$ is greater than the critical value, i.e. when $h_l\geq h_{l;1-\frac{\alpha}{2}}$.</p>

<p style="text-align:justify;">On the other hand, if we want to determine if the observation $X_{max} = max(X_1,\ldots,X_n)$ is an outlier, the Grubbs test is used. The statistic corresponding to this test is defined by the following expression:</p>

\begin{equation}
G=\displaystyle\max_{i=1,\ldots,n}H_i=\displaystyle\max_{i=1,\ldots,n} \frac{X_i-\bar{X}}{S}=\frac{X_{max}-\bar{X}}{S}
\end{equation}

<p style="text-align:justify;">If we want to determine if the smallest observation $X_min = min(X_1,\ldots,Xn)$ is an outlier, the test statistic is:</p>

\begin{equation}
G=\displaystyle\max_{i=1,\ldots,n}-H_i=\displaystyle\max_{i=1,\ldots,n} \frac{X_i-\bar{X}}{S}=\frac{X_{min}-\bar{X}}{S}
\end{equation}

The critical value for this test is defined by:

\begin{equation}
g_{n;1-\alpha}\approx \frac{(n-1)t_{n-2;1-\frac{\alpha}{2}}}{\sqrt{n\left(n-2+t_{n-2;1-\frac{\alpha}{2}^2}\right)}}
\end{equation}

<p style="text-align:justify;">For the special problem where there are $L$ laboratories and n replicates obtained for each one, the statistic $g_{L;1-\alpha}$is defined. In this case, the observations must be replaced by the means of the results corresponding to each laboratory, whereas the mean of the observations is also replaced by the global mean obtained as the mean of laboratories mean.</p>

<p style="text-align:justify;">If a laboratory is identified as an outlier, after applying the $h$ statistic and the Grubbs test to different levels within a laboratory, this is an evidence of the presence of a laboratory high bias (due to a high systematic error in calibration, or errors in the equations when the results were computed).</p>

<br>

### *`r colorize("3.1.2. Mandel's k statistic and Cochran test","#1CA666")`*

```{r setup, warning=FALSE, message=FALSE}
library(ILS)
```
